Flow Specification in GEM5

### 2015-08-23 Flow Specification.tex
k

This two specifications are also symmetric for CPU2.
\end{document}

>>>>

\begin{figure} 
 \centerline{
 \includegraphics[width=1.5in]{figures/storeFail.png}}

 {\footnotesize
 \[
 \begin{array}{llll}
 msg0: (&\mbox{ CPU1},&\mbox{StoreFailedReq},&\mbox{ICache1})\\                   
 msg1: (&\mbox{ ICache1},&\mbox{ StoreFailedRes},&\mbox{ CPU1 })\\
 \end{array}
 \]}
 \caption{Flow specification ($F_2$) of a cache coherent read operation initiated from CPU1 to  data cache}
 \label{storefail}

 \end{figure}
Another flow implemented in GEM5 is when CPU initiate a store failed request to instruction cache, with a simple store failed response from instruction cache. Detailed flow specification is specified in Fig.~\ref{storefail}

This three specifications are also symmetric for CPU2.
\end{document}
